Empirical normative theories

### 2020-07-16 simple.tex
Moved unsatisfactory pref theory to later
Removed more old stuff

@@

\section{Theories proposing decisive arguments}
In most situations, there are too many arguments to attempt to exhaustively test whether any $\ar$ is a decisive argument for any $\phi$. And most importantly, it is impossible to confirm definitely that $(\ar, \ar') \ileadstost \phi$, whenever $(\ar, \ar') \ileadstost \phi$. This is why falsifiable theories are needed.

A theory $T$ proposing decisive arguments describes a set $D_T$ of decision situations to which it applies, and proposes, for any situation $d = (\Phi, \allargs, \ileadstost) \in D_T$, a subset $\Phi_{d, T} \subseteq \Phi$ and a mapping $f_{d, T}: \Phi_{d, T} → \allargs$. The theory claims that it knows the deliberated preference of $i$ (the individual described by $\ileadstost$ in $d$) about the propositions in $\Phi_{d, T}$, and claims that $f_{d, T}(\phi)$ is a decisive argument for $\phi$. The theory $T$ is said to have a position about $\prop$ if $(\prop, \text{sure}) \in \Phi_{d, T} ∨ (¬\prop, \text{possible}) \in \Phi_{d, T}$. 
In order for the claims of the theory to be interpretable, it is requested that if $T$ has a position about $\prop$, then it must have a position about $¬\prop$. This forces $T$, for each pair $(\prop, ¬\prop)$, to either claim that one is sure, claim that both are possible, or have no claim about the pair.

A falsification instance of $T$ is a triplet $(d, \ar', \phi) \in D_T × \allargs × \Phi_{d, T}$ such that $(f_{d, T}(\phi), \ar') \ileadstoe ¬\phi$.
A theory $T$ is said to be falsified iff such a triplet is found.

As is usual in science, falsification procedures should not be considered as ways of definitely validating a theory, but rather as ways of confronting theories.
Two theories $T, T'$ are said to disagree on $\phi$ iff $\phi \in \Phi_{d, T}$ and $¬\phi \in \Phi_{d, T'}$ in some situation $d \in D_T ∪ D_{T'}$. $T$ and $T'$ are said to disagree iff they disagree on some $\phi \in \Phi$.
To confront a theory $T$ to a disagreeing theory $T'$, suffice to test, for any situation $d \in D_T ∪ D_{T'}$ and $\phi$ such that $\phi \in \Phi_{d, T}, ¬\phi \in \Phi_{d, T'}$, whether $(f_{d, T}(\phi), f_{d, T'}(¬\phi)) \ileadstoe \phi$.
Such a test necessarily falsifies one of the theories.

The following proposition shows that this notion of falsification adequately tests the claims of the theory.
\begin{proposition}
	\label{thm:fals}
	A theory $T$ proposing decisive arguments has no falsification instances iff $\forall d \in D_T, \forall \phi \in \Phi_{d, T}: f_{d, T}(\phi)$ is $\phidec$. Furthermore, if a theory $T$ proposing decisive arguments has no falsification instances, then $\Phi_{d, T} \subseteq \iPhi$, $\forall d \in D_T$.
\end{proposition}

\begin{example}[(cont.)]
	Returning to the previous example, a theory $T$ could claim that, for all individuals that belong to some given socio-economic situation and that have some given degree (described by the theory in sufficient details that it is possible to determine precisely to which kind of individuals it applies), $(\prop_a, \text{sure})$ is in the deliberated preferences of the individuals, for a given alternative $\alt$ also described by $T$. 
The theory also suggests some argument $\ar$, a text that (according to $T$) will convince any individual (fitting the description) that $\prop_\alt$ holds, thus, that $\alt$ is a “good” food product for him. 
The theory can be put to the test by picking an individual fitting the description, presenting the argument together with any other argument (for example, proposed by another theory), and observing whether $i$ is convinced.
$T$ resists to such a falsification test if $i$ is convinced. According to \cref{thm:fals}, $T$ tells the truth if it would resist to any possible falsification test. (This is impossible to definitely make sure of.)
\end{example}
This example illustrates a difference between this proposal and the classical revealed approach: it could be that $T$ tells the truth even though its claim does not correspond to the revealed preference of some individuals, thus that, given no argument, some individuals would consider $a$ as dominated by another alternative in the set considered. It also illustrates a difference between this proposal and persuasion: the goal of $T$ is not merely to convince $i$ (possibly by using its lack of knowledge of any counter-argument to what $T$ says), but to resist any falsification attempt. Thus, $T$ should be confronted to arguments coming from as varied perspectives as possible, in order to give confidence that it tells the truth.

@@

\section{Models}
A model is a triple $(\mbeats, \mleadsto, +)$ defined as follows and satisfying the following constraints.

$\mbeats$ a binary relation over $\allargs$. $\mleadsto \subseteq \allargs × \alltopic$. Define $\clargs \subseteq \allargs$ as the set of arguments used in $\mbeats ∪ \mleadsto$. Let $+$ be defined over arguments used in the model: $\ar_3 + \ar_1 = \ar'$ for some $\ar' \in \clargs$, for any $\ar_3, \ar_1 \in \clargs$.

Requirements. The maximum length of a path in $\mbeats$ is finite (which implies that $\mbeats$ is acyclic).
$\ar_3 \mbeats \ar_2 \mbeats \ar_1 ⇒ \ar_2 \mbeats \ar_3 + \ar_1$.\footnote{Necessary for definition of $\ar_3 \wibeatse[\phi] \ar_2$. TODO remove this condition, define $\wibeatse[\phi]$ more largely and never valid when not in $\mbeats$.}

Notation. Let $\mleadstoinv(\alltopic) \subseteq \clargs$ denote the subset of arguments supporting propositions. 
$\mbeats(\args)$: arguments that $\args$ attacks, $\ar_1 \in \mbeats(\args) ⇔ \exists \ar_2 \in \args \suchthat \ar_2 \mbeats \ar_1$; $\mbeatsinv(\ar)$: arguments attacking $\ar$, $\ar_2 \in \mbeatsinv(\ar) ⇔ \ar_2 \mbeats \ar$.  We write $\ar \mleadsto (\prop, \text{possible})$ for $\ar \mleadsto \prop$ and $\ar \mleadsto (\prop, \text{sure})$ for $\ar \mleadsto \prop ∧ (¬\prop \notin \mleadsto(\allargs))$.

Given a decision situation, we define the relations $\wibeatse[\phi], \nwibeatse[\phi] \subseteq \allargs × \allargs$ in order to obtain the following result, and with $\wibeatse[\phi], \nwibeatse[\phi] \subseteq \mbeats$.

Given $\ar_3 \mbeats \ar_2, \phi \in \Phi$: $\ar_3 \wibeatse[\phi] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \nwibeatse[\phi] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe ¬\phi]$.

Given $\ar_3 \mbeats \ar_2, \phi \in \Phi$: $\ar_3 \nwibeatse[\phi] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \wibeatse[\phi] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe \phi]$.

This is done with the following construction.
Given a model. 
\begin{itemize}
	\item Define a root as an argument that $\mbeats$-attacks nothing. 
	\item Associate to each $\ar \in \clargs$ its depth $d(\ar)$, the distance to the farthest root: $d(\ar) = 0$ iff $\ar$ is a root and $d(\ar) = k+1$ iff $\ar$ $\mbeats$-attacks some $\ar'$ of depth $k$ and $\mbeats$-attacks no $\ar'$ of depth superior to $k$. \footnote{Thus $d(\ar) = 1$ iff $\ar$ attacks some and only root nodes; $d(\ar) = 2$ iff $\ar$ attacks some node of depth 1 and only nodes of depth 1 or 0; and so on.} 
	\item Observe that if $\ar_3 \mbeats \ar_2$ and $d(\ar_3) = k+1$, then $d(\ar_2) ≤ k$. 
	\item Define $\wibeatse[\phi]_{(0)} = \nwibeatse[\phi]_{(0)} = \emptyset$. 
	\item Define $\wibeatse[\phi]_{(k+1)} \subseteq \mbeats$, $k ≥ 0$, as $\ar_3 \wibeatse[\phi]_{(k+1)} \ar_2$ iff $\ar_3 \mbeats \ar_2$, $d(\ar_3) = k+1$, and: $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi]_{(d(\ar_2))} \ar_1 ∧ \ar_2 \nwibeatse[\phi]_{(d(\ar_2))} \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe ¬\phi]$. Proceed similarly for $\nwibeatse[\phi]_{(k+1)}$.
	\item Define $\wibeatse[\phi] = \bigcup_{k ≥ 0} \wibeatse[\phi]_{(k)}$, and similarly for $\nwibeatse[\phi]$.
\end{itemize}

Given $\ar_3 \in \clargs, \ar_2 \in \clargs$, with $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\phi] \ar_1$, we have: $\ar_3 \wibeatse[\phi] \ar_2 ∨ \ar_3 \nwibeatse[\phi] \ar_2$.

Define $\ar_2 \wibeatse \ar_1 ⇔ \exists \phi \in \alltopic \suchthat \ar_2 \wibeatse[\phi] \ar_1$.

Hence, given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic)$: $¬ (\ar_3 \nwibeatse \ar_2)$ iff $\forall \ar_1 \in \mbeats(\ar_2) ∩ \wibeatse(\ar_2): ¬ (\ar_2 \wibeatse \ar_3 + \ar_1)$.

\section{Conditions}
All these conditions assume that a decision situation $(\allalts, \allargs, …)$ and a model $\eta = (\mbeats, \mleadsto, +)$ are given.

Define $\argsdec^\phi = \clargs \setminus \text{im}(\wibeatse[\phi])$ the decisive arguments according to $\wibeatse[\phi]$, or $\wibeatse[\phi]$-decisive arguments for short: $\ar \in \argsdec^\phi ⇔ \wibeatseinv[\phi](\ar) = \emptyset$.

We say that $\ar$ replaces $\ar_1$ iff $\mbeats(\ar_1) \subseteq \mbeats(\ar)$.

\begin{definition}[Reinstatement]
	Given $\ar_3 \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1, \ar_3 \in \argsdec^\phi$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
	\footnote{TODO the condition must be $\wibeatseinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$ to allow $\ar_5 \mbeats \ar_4 \mbeats \ar_3 \mbeats \ar_2 \mbeats \ar_1$ and $\ar_5 \mbeats \ar_4 \mbeats \ar_3 + \ar_1$, considering that possibly $\ar_3$ is $\wibeatse$-decisive. This should not invalidate the conditions, but it does currently. But it’s not a problem: the model would actually not be built this way. In this scenario the argument $\ar_3 + \ar_1$ is useful only in case $\ar_3$ is decisive, thus $\ar_4 \mbeats \ar_3 + \ar_1$ must not be planned. Rather $\ar_5 + \ar_3$ decisive, then $(\ar_5 + \ar_3) + \ar_1$. Alternatively, also $\ar_4 \mbeats \ar_1$ and then no problem as well.}
	\footnote{The stronger condition mandating $\mbeatsinv(\ar_3 + \ar_1) \subseteq \wibeatseinv(\ar_1) \setminus \mbeats(\ar_3)$ would be more difficult to check: when some $\ar_2 \wibeatse \ar_3 + \ar_1$, we’d need to check not only that $\ar_2 \mbeats \ar_1$ but also $\ar_2 \wibeatse \ar_1$.}
	\footnote{We do not mandate that $\ar_3 + \ar_1 \ileadsto \phi$, so that the model can afford not resisting to the counter-attacks to $\ar_3 + \ar_1$ (resistance to c-a to $\ar_1$ suffice).}
	\footnote{Is Reinf equivalent to Justifiable unstability? Define $\ar_3 \wibeatsst[\phi] \ar_2 ⇔ \ar_3 \wibeatse[\phi] \ar_2 ∧ ¬(\ar_3 \nwibeatse[\phi] \ar_2)$. Prove that $\ar_3 \wibeatsst[\phi] \ar_2 \wibeatse[\phi] \ar_2 ⇒ ¬(\ar_2 \wibeatse[\phi] \ar_3 + \ar_1)$.} 
\end{definition}

\begin{definition}[Justifiable unstability]
	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse[\phi] \ar_1, \ar_2 \nwibeatse[\phi] \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\phi] \ar_2$.
\end{definition}

$\ar$ is $\phi$-defended iff $\wibeatseinv[\phi](\ar) \subseteq \wibeatse[\phi](\argsdec^\phi)$ (its $\wibeatse[\phi]$-attackers are $\wibeatse[\phi]$-attacked by $\wibeatse[\phi]$-decisive arguments).

\begin{definition}[Finite defense]
	If $\wibeatseinv[\phi](\ar) \subseteq \wibeatse[\phi](\argsdec^\phi)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse[\phi](\args)$.
\footnote{To satisfy Finite defense, in presence of the other conditions, suffice to limit the width of the model (TODO check). But it may be interesting to not limit it and declare that the model has specific replies to any counter-argument, but promises to use only a few rebuttals and that afterwards, the dm will stop using those kind of arguments (but we don’t know in advance which ones will be chosen).}
\end{definition}
Thus, if the attackers of $\ar$ are attacked by decisive arguments, then $j$ defenders are enough to defend $\ar$.

Define $R^\phi$, the reinstates relation, as follows: $(\ar_3 + \ar_1) R^\phi \ar_1$ iff $\ar_3 \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1$ (for some $\ar_2, \phi$), $\ar_3 \in \argsdec^\phi$. Define $\gdargs^\phi$ as the transitive closure of $\mleadstoinv(\Phi)$ under $R^\phi$. Given $\phi, \ar \in \gdargs^\phi, \ar' \in \allargs$, define $\ar' \ibeatse[\phi] \ar ⇔ (\ar', \ar) \ileadstoe ¬\phi$.
\begin{definition}[Covering]
	$\forall \phi, \ar \in \gdargs^\phi, \ar' \in \allargs: \ar' \ibeatse[\phi] \ar ⇒ \ar' \wibeatse[\phi] \ar$. 
\end{definition}

\begin{definition}[Observable validity]
	$\forall \ar_2 \mbeats \ar_1 \mleadsto \phi: ¬(\ar_2 \wibeatse[\phi] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\phi] \ar_2$.
	\footnote{If the model claims $¬\prop \in \isure$, this requires clear-cut (for that prop), so we must mandate it (hopefully A3 or an equivalent such as Justifiable unstability fits). Thus we only need to prove $\prop \notin \iposs$, for which $(\ar_1, \ar) \ileadstose ¬\prop$, for each $\ar$, suffices. In fact, from $\ar_1$ in the model arguing for $\phi$ and $(\ar_1, \ar) \ileadstoe \phi \forall \ar \in \allargs$, we should probably be able, using the argument in the theorem about finite chains, to deduce that this is enough to conclude that $\ar_1$ is $\phidec$.}
\end{definition}

\section{Theorem}
\begin{theorem}[Validity]
	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iPhi$.
\end{theorem}
\begin{proof}
First, we want to prove that $\ar_1$ $\phi$-defended implies $\ar_1$ replaceable by some $\wibeatse[\phi]$-decisive $\ar$, and if $\ar_1 \in \gdargs^\phi$, then its replacer $\ar$ is in $\gdargs^\phi$ as well.

Because $\ar_1$ is $\phi$-defended, $\exists \args \subseteq \argsdec^\phi \suchthat \mbeatsinv(\ar_1) \subseteq \wibeatse[\phi](\args)$, $\args$ finite [Finite defense].

Pick any $\ar_{3, 1} \in \args$ such that $\ar_{3, 1} \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1$ (if there’s none, $\ar_1 \in \argsdec^\phi$ and we’re done). $\ar_{3, 1} + \ar_1$ replaces $\ar_1$, and $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_{3, 1})$ [Reinstatement]. Hence, $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \wibeatse[\phi](\args) \setminus \mbeats(\ar_{3, 1})$. Iterate by picking any $\ar_{3, 2} \in \args$ such that $\ar_{3, 2} \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_{3, 1} + \ar_1$ (if there’s none, $\ar_{3, 1} + \ar_1 \in \argsdec^\phi$ and we’re done) and obtaining $\ar_{3, 2} + (\ar_{3, 1} + \ar_1)$ replacing $\ar_{3, 1} + \ar_1$ (hence, replacing $\ar_1$) with $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \mbeatsinv(\ar_{3, 1} + \ar_1) \setminus \mbeats(\ar_{3, 2})$. Hence, $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \wibeatse[\phi](\args) \setminus \mbeats(\ar_{3, 1}) \setminus \mbeats(\ar_{3, 2})$. Iterating in such a way over the finite set $\args$ will finally yield an element that is $\wibeatse[\phi]$-decisive. The last point, $\ar_1 \in \gdargs^\phi ⇒ \ar \in \gdargs^\phi$, follows from the definition of $\gdargs^\phi$.

Second, we want to prove that if $\ar_1$ is not $\phi$-defended and has no decisive $\wibeatse[\phi]$-attackers (meaning that $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$), then $\ar_1$ is $\wibeatse[\phi]$-attacked by some $\ar_2$ that is not $\phi$-defended and has no decisive $\wibeatse[\phi]$-attacker.

Consider $\ar_1$ not $\phi$-defended and having no decisive $\wibeatse[\phi]$-attackers. Because $\ar_1$ is not $\phi$-defended, by definition, it is $\wibeatse[\phi]$-attacked by some $\ar_2$ that has no decisive $\wibeatse[\phi]$-attacker. Because $\ar_1$ has no decisive attacker, $\ar_2$ is not decisive. If $\ar_2$ was defended, by the first part of this proof, it would be replaceable by a decisive argument, and $\ar_1$ would have a decisive attacker. Thus, $\ar_2$ is not defended.

We conclude from this second point that if $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$, then $\ar_1$ is $\phi$-defended. Otherwise, it would be attacked by some $\ar_2$, on which the condition would apply in turn, thus which would be attacked by some $\ar_3$, on which the condition would apply, and iterating in this way would build an infinite chain in $\wibeatse[\phi]$, a contradiction.

Third, consider an argument $\ar_1 \in \mleadstoinv(\Phi)$. If some $\ar_2 \wibeatse[\phi] \ar_1$ then $\ar_3 \wibeatse[\phi] \ar_2$ [Obs val]. Thus, $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$. Thus, $\ar_1$ is $\phi$-defended, by our second point. Hence, by our first point in this proof, $\ar_1$ is replaceable by some $\wibeatse[\phi]$-decisive $\ar \in \gdargs$. We obtain that $\forall \ar' \in \allargs: ¬(\ar' \wibeatse[\phi] \ar)$. As $\ar \in \gdargs$, $\ar' \ibeatse[\phi] \ar ⇒ \ar' \wibeatse[\phi] \ar$ [Covering], thus we obtain $¬(\ar' \ibeatse[\phi] \ar)$, hence $\ar$ is $\phidec$ and $\phi \in \iPhi$.
\end{proof}

\appendix
\section{Todo}
We define $(\ar, \ar') \ileadstopst \prop ⇔ \ar' \nibeatsst[\prop] \ar ⇔ \ileadsto(\ar, \ar') \subseteq \{\propsure, b\}$, and $(\ar, \ar') \ileadstosst ¬\prop ⇔ \ar \nibeatsst[¬\propsure] \ar' ⇔ \ileadsto(\ar, \ar') = \{¬\propsure\}$.
Hence, $(\ar, \ar') \ileadstose ¬\prop ⇔ \ar' \ibeatse[\prop] \ar ⇔ ¬(\ar' \nibeatsst[\prop] \ar) ⇔ \ileadsto(\ar, \ar') \supseteq \{¬\propsure\}$, and $(\ar, \ar') \ileadstope \prop ⇔ \ar \ibeatse[¬\propsure] \ar' ⇔ ¬(\ar \nibeatsst[¬\propsure] \ar') ⇔ \ileadsto(\ar, \ar') ≠ \{¬\propsure\}$.

\begin{itemize}
	\item If $i$ does not consider $\ar$ as supporting $\prop$, it also works: if $\prop$ is not weakly acceptable by default, then any $\ar'$ is considered by $i$ as a better argument than $\ar$ in favor of certain $¬\prop$, and so on. In fact, whether $\emptyset \ibeatse[\prop] \emptyset$ determines whether $\prop$ is weakly supported by default.
	\item I should define $\ar' (□\ibeatse[\prop]) \ar$ as an observable: “Assuming $\ar'$ would survive, do you consider $\ar'$ as leading to certainty of $¬\prop$, even when considering $\ar$?”. It distinguishes our knowledge and the truth: $\ar' (□\ibeatse[\prop]) \ar ⇒ \ar' \ibeatse[\prop] \ar$, thus, implies $¬ (\ar' \nibeatsst[\prop] \ar)$. But out of $¬ (\ar' (□\ibeatse[\prop]) \ar)$, nothing.
	\item Partition (objectively) $\allargs$ (or $\allargs × \alltopic$) into arguments in favor of $\prop, \text{sure}$, $¬\prop, \text{sure}$, and similarly for possible. Use only one rel $\ibeatse$, defined on contradictory arguments only, instead of $\ibeatse[\prop, \text{sure}]$ and others. Define $\ar' \ibeatse[\prop] \ar$ equals no when $¬(\ar' \ileadsto ¬\prop, \text{sure})$, equals $\ibeatse$ for adequate arguments, and equals yes when $¬(\ar \ileadsto \prop, \text{possible})$ and $\ar' \ileadsto ¬\prop, \text{sure}$, with probably some complications needed for the argument $\emptyset$ (and related default attitude towards $\prop$).
\end{itemize}

Questions:
Q1. Relationship with $\ar \ibeatse[\prop] \ar$?

We want to exclude: $s$ supports $p$ perhaps, attacked by $s2$ (supporting $¬p$ sure), but then $s2$ is attacked by $s$. Exclude $\ar' \ibeatse[\prop] \ar$ and $\ar \ibeatse[¬\prop, \text{sure}] \ar'$. Require to assume that this situation implies another argument $\ar_3$ “attacking” $\ar'$, thus, such that $\ar_3 + \ar$ is no more attacked by $\ar_2$.

\subsection{Attack rel}
Given $\prop$, define a (symmetric) strong attack rel, $Q_\prop$, as $\ar Q_\prop \ar'$ iff $(\ar, \ar') \ileadstosst ¬\prop$.

Define a (symmetric) weak attack rel, $R_\prop$, as $\ar R_\prop \ar'$ iff $(\ar, \ar') \ileadstopst ¬\prop$.

Given $\prop$, we want to check the arguments that defend it. We want to build an asymmetric attack relation.
$\ar_1 M \ar_0$, and not the converse, iff $\ar_1$ attacks $\ar_0$ and, would $\ar_1$ be attacked, $\ar_0$ reinstated would defend $\prop$.
$\ar_1$ should be able to support a sub-claim $\prop'$, and then $\ar_2$ attack $\ar_1$ on that sub-claim precisely. $\ar_2$ decisive on this sub-claim and $\ar_0 + \ar_2$ decisive implies $\ar_1$ attacks $\ar_0$ and not conversely.

Or simply. $\ar_1$ decisive for $¬\prop$ means $\ar_1$ attacks $\ar_0$ and not conversely.

Then define $i$’s DJ in terms of argumentation semantics.

\section{To think}
Propositions weakly self-supported $T \subseteq \alltopic$: weakly accepted if no arg is given. Examples: $m$ = “eat miam”; $¬b$ = “beurk is to exclude”; or, in a problem where there’s no particularly good aliments, both $a$ = “eat this” and $¬a$.

When given $(\ar, \prop)$, $i$ may say: $\ar$ does not survive; or: assuming $\ar$ survives, then $\ar$ supports $\prop$, or, assuming $\ar$ survives, then $\ar$ does not support $\prop$ anyway.

When given $\ar'$ against $\ar$, $i$ may say: $\ar'$ does not survive, or: assuming $\ar'$ survives, then $\ar'$ supports $¬\prop$, …

Given $(\ar_2, \prop), (\ar_1, ¬\prop) \in D$, define $¬(\ar_2 \wibeatse^\text{neg}_{¬\prop} \ar_1)$ iff for some $(\ar, \prop) \in D$, where $\ar_1 \ibeatse[\prop] \ar$: $\ar_1 \ibeatse[\prop] \ar + \ar_2$. Equivalently: $\ar_2 \wibeatse^\text{neg}_{¬\prop} \ar_1$ iff for all $\ar$, where $\ar_1 \ibeatse[\prop] \ar$: $¬(\ar_1 \ibeatse[\prop] \ar + \ar_2)$. (This does not seem right: if given $\ar_3$ attacking $\ar_2$, and not given $\ar_4$ which would convincingly rebut $\ar_3$, then temporarily it may hold again that $\ar_1 \ibeatse[\prop] \ar + \ar2$ (in the sense that $\ar_1 + \ar_3 \ibeatse[\prop] \ar + \ar_2$).)

$\ar_2 \wibeatse_{¬\prop} \ar_1$ can perhaps be queried directly by asking (in the context of some $\ar_1 \ibeatse[\prop] \ar$): “assume $\ar_2$ survives, then does $\ar_2$ counter $\ar_1$?” (In the sense that $\ar_2$ is sufficiently convincing that $\prop$ holds perhaps, to cancel the argument $\ar_1$ according to which $¬\prop$ surely holds.)

\section{Certainties}
Looking for certainties. Those propositions that are in the reflexive preferences in a demanding sense: there is a strong enough reason to prefer it than its contrary.
\begin{itemize}
	\item $\ar' \wibeatse \ar$: weak attack; $\ar'$ renders $\ar$ invalid (can’t be used to say that $t$ holds for sure) (assuming $\ar'$ survives)
	\item Propositions strongly self-supported: strongly accepted if no arg is given. Examples: $m$ = “eat miam”; $¬b$ = “beurk is to exclude”. We might have neither $c$ nor $¬c$ in that set.
\end{itemize}

\begin{definition}[Sure acceptance]
	Define a situation $(\allalts, \allargs, \set{\ibeatse[\prop]})$. A proposition $\prop \in \alltopic$ is accepted as sure iff $\exists \ar' \in \allargs \suchthat \forall \ar \in \allargs: \ar \nibeatsst[\prop, \text{sure}] \ar'$.
\end{definition}

Assume we use rather: if $p$ is not sure, then $¬p$ is weakly accepted (by def). Then we have never problems of inconsistency! But we could be in a situation where $p$ is not accepted as sure but nobody can tell why because it is fundamentally unstable (sometimes $p$ being accepted, sometimes not).

\section{Example about model instanciation}
The general conditions are Reinstatement, Justifiable unstability, Finite defense and Covering.
A general model is a model that claims it satisfies the general conditions.

TODO give up general models. In this example, $\ar_1$ would need to be planned as attacking sometimes $\ar_2$. Better consider an instanciation mechanism. An instantiated model is particular, and can be tested (especially against another one).
\begin{example}
	$\ar_3 \mbeats \ar_2 \mbeats \ar_1 \mleadsto \prop$, $\ar_2 \mleadsto ¬\prop$; $\ar_3 + \ar_1 \mleadsto \prop$.
\end{example}
This model is compatible (meaning that it satisfies the general conditions) with the following decision situations. We describe $\ibeatse$ fully (no attack iff not mentioned).
\begin{itemize}
	\item Sure of $\prop$: $\ar_1 \mleadsto \prop$; $\ar_3 \ibeatse \ar_2$ (the rest is implied, for example $\forall \ar_4 \in \allargs: \ar_1 \ibeatse[¬\prop] \ar_4$ because of covering).
	\item Sure of $\prop$ with reinstatement: $\ar_3 \ibeatse[\prop] \ar_2 \ibeatse[\prop] \ar_1 \mleadsto \prop$; $\ar_1 + \ar_3 \mleadsto \prop$; $\ar_3 \ibeatse[¬\prop] \ar_2$
	\item Sure of $¬\prop$: $\ar_2 \mleadsto ¬\prop$; $\ar_2 \ibeatse \ar_1$
	\item Both: $¬(\ar_2 \ibeatse \ar_1), \ar_1 \mleadsto \prop$, $¬(\ar_3 \ibeatse \ar_2), \ar_2 \mleadsto ¬\prop$
\end{itemize}
This situation falsifies the model. $\ar_4 \ibeatse \ar_1$, $\ar_4$ not attacked.

\section{Model certainties}
Assume we define $\ar_1 \wibeatse[¬\prop, \text{sure}] \ar_2 ⇔ \ar_2 \nwibeatse[\prop] \ar_1$. Then, indeed, given $\ar_1 \mleadsto \prop$, $\ar_2 \wibeatse[¬\prop, \text{sure}] \ar_1 ⇔ \ar_2 \ibeatse[¬\prop, \text{sure}] \ar_1$. But it gives the wrong conclusion. For $\ar_3 \mbeats \ar_2 \mbeats \ar_1 \mleadsto t: \ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\ar_2 \nwibeatse[¬\prop] \ar_3$ iff $\exists \ar_1 \in \mbeats(\ar_3) \suchthat \ar_3 \wibeatse[¬\prop] \ar_1 ∧ \ar_3 \wibeatse[¬\prop] \ar_2 + \ar_1$.

Given $\ar_1 \mleadsto \prop$, define $\ar_2 \wibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_2 \ibeatse[\prop, \text{sure}] \ar_1$.

Given $\ar_1 \mleadsto \prop$, define $\ar_2 \nwibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_1 \ibeatse[¬\prop] \ar_2$.

Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \nwibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.

Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \nwibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \wibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.

\section{Example about default arguments}
s2 argues in favor of p against s1: s "le monde n’est pas fiable". s1 "le monde est fiable, bhl l’a dit". s2 "bhl est un clown, il s’est planté sur l’Irak". s3 "il avait raison sur l’Irak : l’Irak a des ADM". s4 "l’Irak n’a pas d’ADM, Bush l’a reconnu".
Does s4 attack s3?
"bhl est un clown, il s’est planté sur l’irak" + "l’irak n’a pas d’ADM, Bush l’a reconnu" VS "il avait raison sur l’Irak : l’Irak a des ADM" !

Measure problem?

\section{Alternative definitions of finite defense}
Define Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec as: $\wibeatseinv(\ar) \subseteq \wibeatse(\clargs \setminus \text{im}(\mbeats)) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args)$. Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is insufficient to provide $T_\eta = \iposs$. Define $\ar' \mbeats^\text{fail} \ar$ iff $\ar' \mbeats \ar ∧ ¬(\ar' \wibeatse \ar)$. Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$, $\ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar_4 \mbeats^\text{fail} \{\ar_3, \ar_3', …\}$. Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is artificially satisfied because the antecedent fails to trigger.

>>>>

\subsection{Example}
\begin{example}[(cont.)]
	Returning to the previous example, a theory $T$ could claim that, for all individuals that belong to some given socio-economic situation and that have some given degree (described by the theory in sufficient details that it is possible to determine precisely to which kind of individuals it applies), $(\prop_a, \text{sure})$ is in the deliberated preferences of the individuals, for a given alternative $\alt$ also described by $T$. 
The theory also suggests some argument $\ar$, a text that (according to $T$) will convince any individual (fitting the description) that $\prop_\alt$ holds, thus, that $\alt$ is a “good” food product for him. 
The theory can be put to the test by picking an individual fitting the description, presenting the argument together with any other argument (for example, proposed by another theory), and observing whether $i$ is convinced.
$T$ resists to such a falsification test if $i$ is convinced. According to a previous theorem, $T$ tells the truth if it would resist to any possible falsification test. (This is impossible to definitely make sure of.)
\end{example}
This example illustrates a difference between this proposal and the classical revealed approach: it could be that $T$ tells the truth even though its claim does not correspond to the revealed preference of some individuals, thus that, given no argument, some individuals would consider $a$ as dominated by another alternative in the set considered. It also illustrates a difference between this proposal and persuasion: the goal of $T$ is not merely to convince $i$ (possibly by using its lack of knowledge of any counter-argument to what $T$ says), but to resist any falsification attempt. Thus, $T$ should be confronted to arguments coming from as varied perspectives as possible, in order to give confidence that it tells the truth.

@@

@@
